Moral Foundations of U.S. Political News Organizations

### 2019-03-02 pilot_manuscript.Rmd
set up some scraping stuff. Will resume tomorrow

library(rvest)
####NY Times####
#Specifying the url for desired website to be scrapped
url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'

@@

>>>>

library(rvest)
####NY Times####
#Specifying the url for desired website to be scraped
url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'

@@

````{r NPR, eval = F, include = F}
url2 = 'https://www.npr.org/search?query=kavanaugh&page=1'
webpage2 = read_html(url2)
headline_data2 = html_nodes(webpage2,'.title .ais-Highlight-nonHighlighted')

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist2[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
} ##end for loop
```

````{r Slate, eval = F, include = F}
url3 = 'https://slate.com/search?q=kavanaugh&via=homepage_nav_search'
webpage3 = read_html(url3)
headline_data3 = html_nodes(webpage3,'.gs-title')

#URLs
attr_data3 = html_attrs(headline_data3) 
attr_data3

urlslist3 = unlist(attr_data3)
urlslist3 = urlslist3[grep("http", urlslist3)]
urlslist3

##start a data frame
SlateDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(SlateDF) = c("Source", "Url", "Text")
SlateDF = as.data.frame(SlateDF)

  ##pull the specific nodes
  headline_data3 = html_nodes(webpage3,'.slate-paragraph')

  ##save the data
  SlateDF$Source[i] = "Slate"
  SlateDF$Url[i] = urlslist3[i]
  SlateDF$Text[i] = paste(text_data3, collapse = "")
} ##end for loop
```

````{r HuffPo, eval = F, include = F}
url4 = 'https://search.huffingtonpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s'
webpage4 = read_html(url4)
headline_data4 = html_nodes(webpage4,'.fw-b')

#URLs
attr_data4 = html_attrs(headline_data4) 
attr_data4

urlslist4 = unlist(attr_data4)
urlslist4 = urlslist4[grep("http", urlslist4)]
urlslist4

##start a data frame
HuffpoDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
colnames(HuffpoDF) = c("Source", "Url", "Text")
HuffpoDF = as.data.frame(HuffpoDF)

  ##pull the specific nodes
  headline_data4 = html_nodes(webpage4,'p')

  ##save the data
  HuffPoDF$Source[i] = "Huffington Post"
  HuffpoDF$Url[i] = urlslist4[i]
  HuffpoDF$Text[i] = paste(text_data4, collapse = "")
} ##end for loop
```

````{r Politico, eval = F, include = F}
url5 = 'https://www.politico.com/search?q=kavanaugh&s=newest'
webpage5 = read_html(url5)
headline_data5 = html_nodes(webpage5,'.summary a')

##start a data frame
PoliticoDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
colnames(PoliticoDF) = c("Source", "Url", "Text")
PoliticoDF = as.data.frame(PoliticoDF)

  ##pull the specific nodes
  headline_data5 = html_nodes(webpage5,'.story-text > p')

  ##save the data
  PoliticoDF$Source[i] = "Politico"
  PoliticoDF$Url[i] = urlslist5[i]
  PoliticoDF$Text[i] = paste(text_data5, collapse = "")
} ##end for loop
```

````{r Fox News, eval = F, include = F}
url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&sort=latest&start=0'
webpage6 = read_html(url6)
headline_data6 = html_nodes(webpage6, 'h3 .ng-binding')

attr_data6 = html_attrs(headline_data6) 
attr_data6

urlslist6 = unlist(attr_data6)
urlslist6 = urlslist6[grep("http|.html", urlslist6)]

##start a data frame
FoxDF = matrix(NA, nrow = length(urlslist6), ncol = 3)
colnames(FoxDF) = c("Source", "Url", "Text")
FoxDF = as.data.frame(FoxDF)

##for loops
for (i in 1:length(urlslist6)){

  ##read in the URL
  webpage6 <- read_html(urlslist6[i])

  ##pull the specific nodes
  headline_data6 = html_nodes(webpage6,'p+ p , .fn-video+ p , .twitter+ p , .speakable')

  ##pull the text
  text_data6 = html_text(headline_data6)

  ##save the data
  FoxDF$Source[i] = "Fox News"
  FoxDF$Url[i] = urlslist6[i]
  FoxDF$Text[i] = paste(text_data6, collapse = "")
} ##end for loop
```

````{r Breitbart, eval = F, include = F}
url7 = 'http://www.breitbart.com/big-government/'
webpage7 = read_html(url7)
headline_data7 = html_nodes(webpage7, '.gs-title')

attr_data7 = html_attrs(headline_data7) 
attr_data7

urlslist7 = unlist(attr_data7)
urlslist7 = urlslist4[grep(urlslist7)]

##start a data frame
BreitbartDF = matrix(NA, nrow = length(urlslist7), ncol = 3)
colnames(BreitbartDF) = c("Source", "Url", "Text")
BreitbartDF = as.data.frame(BreitbartDF)

##for loops
for (i in 1:length(urlslist7)){

  ##read in the URL
  webpage7 <- read_html(urlslist7[i])

  ##pull the specific nodes
  headline_data7 = html_nodes(webpage7,'p , h2')

  ##pull the text
  text_data7 = html_text(headline_data7)

  ##save the data
  BreitbartDF$Source[i] = "Breitbart"
  BreitbartDF$Url[i] = urlslist7[i]
  BreitbartDF$Text[i] = paste(text_data7, collapse = "")
} ##end for loop
```

````{r Rush Limbaugh, eval = F, include = F}
url8 = 'https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1'
webpage8 = read_html(url8)
headline_data8 = html_nodes(webpage8, '.ais-hits--content a')

attr_data8 = html_attrs(headline_data8) 
attr_data8

urlslist8 = unlist(attr_data8)
urlslist8 = urlslist8[grep(urlslist8)]

##start a data frame
RushDF = matrix(NA, nrow = length(urlslist8), ncol = 3)
colnames(RushDF) = c("Source", "Url", "Text")
RushDF = as.data.frame(RushDF)

##for loops
for (i in 1:length(urlslist8)){

  ##read in the URL
  webpage8 <- read_html(urlslist8[i])

  ##pull the specific nodes
  headline_data8 = html_nodes(webpage8,'p')

  ##pull the text
  text_data8 = html_text(headline_data8)

  ##save the data
  RushDF$Source[i] = "Rush Limbaugh"
  RushDF$Url[i] = urlslist8[i]
  RushDF$Text[i] = paste(text_data8, collapse = "")
} ##end for loop
```

````{r Blaze, eval = F, include = F}
url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
webpage9 = read_html(url9)
headline_data9 = html_nodes(webpage9, '.widget__headline-text')

attr_data9 = html_attrs(headline_data9) 
attr_data9

urlslist9 = unlist(attr_data9)
urlslist9 = urlslist9[grep(urlslist9)]

##start a data frame
BlazeDF = matrix(NA, nrow = length(urlslist9), ncol = 3)
colnames(BlazeDF) = c("Source", "Url", "Text")
BlazeDF = as.data.frame(BlazeDF)

##for loops
for (i in 1:length(urlslist9)){

  ##read in the URL
  webpage9 <- read_html(urlslist9[i])

  ##pull the specific nodes
  headline_data9 = html_nodes(webpage9,'p')

  ##pull the text
  text_data9 = html_text(headline_data9)

  ##save the data
  BlazeDF$Source[i] = "The Blaze"
  BlazeDF$Url[i] = urlslist9[i]
  BlazeDF$Text[i] = paste(text_data9, collapse = "")
} ##end for loop
```

````{r Sean Hannity, eval = F, include = F}
url10 = 'https://www.theblaze.com/search/?q=kavanaugh'
webpage10 = read_html(url10)
headline_data10 = html_nodes(webpage10, '.gs-title')

attr_data10 = html_attrs(headline_data10) 
attr_data10

urlslist10 = unlist(attr_data10)
urlslist10 = urlslist10[grep(urlslist10)]

##start a data frame
SeanDF = matrix(NA, nrow = length(urlslist10), ncol = 3)
colnames(SeanDF) = c("Source", "Url", "Text")
SeanDF = as.data.frame(SeanDF)

##for loops
for (i in 1:length(urlslist10)){

  ##read in the URL
  webpage10 <- read_html(urlslist10[i])

  ##pull the specific nodes
  headline_data10 = html_nodes(webpage10,'p')

  ##pull the text
  text_data10 = html_text(headline_data10)

  ##save the data
  SeanDF$Source[i] = "Sean Hannity"
  SeanDF$Url[i] = urlslist10[i]
  SeanDF$Text[i] = paste(text_data10, collapse = "")
} ##end for loop
```
